### 2019-06-13 2-Chapters/3-Chapter/chapter3.tex
\allowdisplaybreaks{} command from https://tex.stackexchange.com/a/12561/97964

\textbf{References.}
%
The code for SMPyBandits is hosted at \texttt{\href{https://GitHub.com/SMPyBandits/SMPyBandits/}{GitHub.com/SMPyBandits/SMPyBandits}}, its documentation is at \texttt{\href{https://SMPyBandits.GitHub.io/}{SMPyBandits.GitHub.io}} or \texttt{\href{https://SMPyBandits.RTFD.io/}{SMPyBandits.RTFD.io}}, and all the library is freely publicly released under the MIT open-source License.
This chapter is based on our article \cite{SMPyBanditsJMLR}.

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_a_IndexPolicy_UCB.py}
    % \caption{Small snippet of code defining the UCB algorithm, as a simple example of an Index Policy}
    \captionof{listing}{Small snippet of code defining the UCB algorithm, as a simple example of an Index Policy\label{lst:3:smallIndexPolicy}.}
    % \label{lst:3:smallIndexPolicy}
% \end{listing}
\end{small}

@@

\begin{figure}[h!]  % [htbp]
    \centering
	\includegraphics[width=0.49\linewidth]{overview_documentation_1.png}
    \includegraphics[width=0.49\linewidth]{overview_documentation_2.png}
	\caption{Screenshots from two pages of the documentation.}
	\label{fig:3:twoScreenshotsOfTheDocumentation}
\end{figure}

\begin{figure}[h!]  % [htbp]
    \centering
	\includegraphics[width=0.49\linewidth]{overview_documentation_3.png}
	\includegraphics[width=0.49\linewidth]{overview_documentation_4.png}
	\caption{Screenshots from two other pages of the documentation.}
	\label{fig:3:twoMoreScreenshotsOfTheDocumentation}
\end{figure}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
    \begin{listing}[h!]
        \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
# 1. get the code in the folder you want
$ git clone https://GitHub.com/SMPyBandits/SMPyBandits.git
$ cd SMPyBandits.git
# 2. install the requirements
$ pip install -r requirements.txt
        \end{minted}
        \caption{Small snippet of Bash code to download and install dependencies of SMPyBandits.}
        % \captionof{listing}{Small snippet of Bash code to download and install dependencies of SMPyBandits \label{lst:3:howToInstallLibrary}.}
        \label{lst:3:howToInstallLibrary}
    \end{listing}
\end{small}

% https://tex.stackexchange.com/a/12430/
\begin{small}
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
# 3. run a single-player simulation
$ BAYES=False ARM_TYPE=Bernoulli N=1000 T=10000 K=9 N_JOBS=4 \
  MEANS=[0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9] \
  python3 main.py configuration.py
    \end{minted}
    \caption{Small snippet of Bash code to run a simple experiment with SMPyBandits.}
    % \captionof{listing}{Small snippet of Bash code to run a simple experiment with SMPyBandits \label{lst:3:howToRunBasicLibrary}.}
    \label{lst:3:howToRunBasicLibrary}
\end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}
configuration["policies"] = [
  {"archtype": klUCB, "params": {"klucb": klucbBern}},
  {"archtype": klUCBPlusPlus,
   "params": {"horizon": T, "klucb": klucbBern}},
  {"archtype": UCBalpha, "params": {"alpha": 1}},
  {"archtype": Thompson, "params": {"posterior": Beta}}
]
    \end{minted}
    \caption{Small snippet of Python code to configure the list of algorithms tested on a problem.}
    % \captionof{listing}{Small snippet of Python code to configure the list of algorithms tested on a problem. \label{lst:3:howToConfigureAlgorithms}.}
    \label{lst:3:howToConfigureAlgorithms}
\end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
    % \caption{Small example of \texttt{main.py} file}
    \captionof{listing}{Small example of \texttt{main.py} file\label{lst:3:main}.}
    % \label{lst:3:main}
% \end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
$ T=50000 N=100 K=10 ARM_TYPE=Gaussian python main.py
    \end{minted}
    \caption{Small snippet of Bash code to run an experiment}
    % \captionof{listing}{Small snippet of Bash code to run an experiment \label{lst:3:howToRunExperiment2}.}
    \label{lst:3:howToRunExperiment2}
\end{listing}

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
    % \caption{Small example of \texttt{configuration.py} file}
    \captionof{listing}{Small example of \texttt{configuration.py} file\label{lst:3:configuration}.}
    % \label{lst:3:configuration}
% \end{listing}
\end{small}

>>>>

\textbf{References.}
%
The code for SMPyBandits is hosted at \texttt{\href{https://GitHub.com/SMPyBandits/SMPyBandits/}{GitHub.com/SMPyBandits/SMPyBandits}}, its documentation is at \texttt{\href{https://SMPyBandits.GitHub.io/}{SMPyBandits.GitHub.io}}, and all the library is freely publicly released under the MIT open-source License.
This chapter is based on our article \cite{SMPyBanditsJMLR}.

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_a_IndexPolicy_UCB.py}
    % \caption{Small snippet of code defining the UCB algorithm, as a simple example of an Index Policy}
    \captionof{listing}{Code defining the UCB algorithm, as a simple example of an Index Policy\label{lst:3:smallIndexPolicy}.}
    % \label{lst:3:smallIndexPolicy}
% \end{listing}
\end{small}

@@

\begin{figure}[h!]  % [htbp]
    \centering
	\includegraphics[width=0.499\linewidth]{overview_documentation_1.png}
    \includegraphics[width=0.499\linewidth]{overview_documentation_2.png}
	\caption{Screenshots from two pages of the documentation: homepage, and list of algorithms in the \texttt{Policies} module.}
	\label{fig:3:twoScreenshotsOfTheDocumentation}
\end{figure}

\begin{figure}[h!]  % [htbp]
    \centering
	\includegraphics[width=0.499\linewidth]{overview_documentation_3.png}
	\includegraphics[width=0.499\linewidth]{overview_documentation_4.png}
	\caption{Screenshots from two other pages of the documentation: the \texttt{klUCBSwitch} policy, and documentation of the API to add a new policy.}
	\label{fig:3:twoMoreScreenshotsOfTheDocumentation}
\end{figure}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
    \begin{listing}[h!]
        \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
# 1. get the code in the folder you want
$ git clone https://GitHub.com/SMPyBandits/SMPyBandits.git
$ cd SMPyBandits.git
# 2. install the requirements
$ pip install -r requirements.txt
        \end{minted}
        \caption{Example of Bash code to download and install dependencies of SMPyBandits.}
        % \captionof{listing}{Small snippet of Bash code to download and install dependencies of SMPyBandits \label{lst:3:howToInstallLibrary}.}
        \label{lst:3:howToInstallLibrary}
    \end{listing}
\end{small}

% https://tex.stackexchange.com/a/12430/
\begin{small}
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
# 3. run a single-player simulation
$ BAYES=False ARM_TYPE=Bernoulli N=1000 T=10000 K=9 N_JOBS=4 \
  MEANS=[0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9] \
  python3 main.py configuration.py
    \end{minted}
    \caption{Example of Bash code to run a simple experiment with SMPyBandits.}
    % \captionof{listing}{Small snippet of Bash code to run a simple experiment with SMPyBandits \label{lst:3:howToRunBasicLibrary}.}
    \label{lst:3:howToRunBasicLibrary}
\end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}
configuration["policies"] = [
  {"archtype": klUCB, "params": {"klucb": klucbBern}},
  {"archtype": klUCBPlusPlus,
   "params": {"horizon": T, "klucb": klucbBern}},
  {"archtype": UCBalpha, "params": {"alpha": 1}},
  {"archtype": Thompson, "params": {"posterior": Beta}}
]
    \end{minted}
    \caption{Example of Python code to configure the list of algorithms tested on a problem.}
    % \captionof{listing}{Small snippet of Python code to configure the list of algorithms tested on a problem. \label{lst:3:howToConfigureAlgorithms}.}
    \label{lst:3:howToConfigureAlgorithms}
\end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
    % \caption{Small example of \texttt{main.py} file}
    \captionof{listing}{Example of \texttt{main.py} file\label{lst:3:main}.}
    % \label{lst:3:main}
% \end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
$ T=50000 N=100 K=10 ARM_TYPE=Gaussian python main.py
    \end{minted}
    \caption{Example of Bash code to run an experiment}
    % \captionof{listing}{Small snippet of Bash code to run an experiment \label{lst:3:howToRunExperiment2}.}
    \label{lst:3:howToRunExperiment2}
\end{listing}

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
    % \caption{Small example of \texttt{configuration.py} file}
    \captionof{listing}{Example of \texttt{configuration.py} file\label{lst:3:configuration}.}
    % \label{lst:3:configuration}
% \end{listing}
\end{small}
